Type cones of $\b{g}$-vector fans

### 2019-04-02 thirdPaper/draft/typeConeAssociahedra.tex

\begin{corollary}
 Assume that~$\ind(\cat)$ is finite.  Let~$X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X$ be a triangle with~$h\in (\susp T)$.  Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b g$ is a non-negative linear combination of the~$\ell_A$, with~$A\in \ind(\cat)\ssm \add(\susp T)$.
\end{corollary}
\begin{proof}
 We know that~$x=\sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, [A] \rangle}{\langle \ell_A, [A] \rangle} \ell_A$; since~$\langle \ell_A, [A] \rangle$ is positive by Lemma~\ref{lemm::bilinear-form}, we only need to show that each~$\langle x, [A] \rangle$ is non-negative. 
 The functor~$F=\cat(T,-)$ induces an exact sequence
 \[
  FX \to FE \to FY \to 0,
 \]
 which in turn induces an exact sequence
 \[
  0\to \Hom{\Lambda}(FY, FA) \to \Hom{\Lambda}(FE, FA) \xrightarrow{f} \Hom{\Lambda}(FX, FA) \to \coker(f) \to 0.
 \]
 Therefore~$\langle x, [A] \rangle = \dim_{\field} \coker(f) \geq 0$.
\end{proof}

@@

\begin{proof}[Proof of Theorem~\ref{theorem::extricats}]\yann{PG: Est-ce que cela te semble suffisant, ou veux-tu que j'ajoute des d\'etails ? }
 The proof is now similar to the proof of Theorem~\ref{theo::relations-g-vecteurs}, by using Proposition~\ref{prop::KRextricat} instead of Proposition~\ref{prop::functor-F}, Proposition~\ref{prop::index iso extricat} instead of Corollary~\ref{coro::grothendieck-g-vectors}, and the fact that~$\tc$ is made of projective objects instead of Lemma~\ref{lemm::almost-split}.
\end{proof}

\begin{proof}[Proof of Corollary~\ref{corollary::meshes positively generate extricats}]
\yann{TO DO}
\end{proof}

@@

\begin{corollary}
 Generalised cluster categories with infinite dimensional Hom-spaces ?
\end{corollary}

>>>>

\begin{corollary}\label{corollary::meshes positively generate cluster cats}
 Assume that~$\ind(\cat)$ is finite.  Let~$X\xrightarrow{} E \xrightarrow{} Y \xrightarrow{h} \susp X$ be a triangle with~$h\in (\susp T)$.  Then the element~$x=[X]+[Y]-[E]$ of the kernel of~$\b g$ is a non-negative linear combination of the~$\ell_A$, with~$A\in \ind(\cat)\ssm \add(\susp T)$.
\end{corollary}
\begin{proof}
 We know that~$x=\sum_{A\in \ind(\cat) \ssm \add(\susp T)} \frac{\langle x, [A] \rangle}{\langle \ell_A, [A] \rangle} \ell_A$; since~$\langle \ell_A, [A] \rangle$ is positive by Lemma~\ref{lemm::bilinear-form}, we only need to show that each~$\langle x, [A] \rangle$ is non-negative. 
 The functor~$F=\cat(T,-)$ induces an exact sequence
 \[
  FX \to FE \to FY \to 0,
 \]
 which in turn induces an exact sequence
 \[
  0\to \Hom{\Lambda}(FY, FA) \to \Hom{\Lambda}(FE, FA) \xrightarrow{f} \Hom{\Lambda}(FX, FA) \to \coker(f) \to 0.
 \]
 Therefore~$\langle x, [A] \rangle = \dim_{\field} \coker(f) \geq 0$.
\end{proof}

@@

\begin{proof}[Proof of Theorem~\ref{theorem::extricats}]
 The proof is now similar to the proof of Theorem~\ref{theo::relations-g-vecteurs}, by using Proposition~\ref{prop::KRextricat} instead of Proposition~\ref{prop::functor-F}, Proposition~\ref{prop::index iso extricat} instead of Corollary~\ref{coro::grothendieck-g-vectors}, and the fact that~$\tc$ is made of projective objects instead of Lemma~\ref{lemm::almost-split}.
\end{proof}

\begin{proof}[Proof of Corollary~\ref{corollary::meshes positively generate extricats}]
The proof is similar to that of Corollary~\ref{corollary::meshes positively generate cluster cats}.
\end{proof}

@@

% \begin{corollary}
%  Generalised cluster categories with infinite dimensional Hom-spaces ?
% \end{corollary}
